Korea Stock Market, centered on Samsung Electronics by Daniel Jang
========================================================

Samsung Electronics, the company of Galaxy series cell-phone manufacturer 
in Korea, https://finance.yahoo.com/quote/005935.KS?p=005935.KS, is said to 
account for 20% of total Korea stock market - the market capitalization 
of Samsung Electronics is 329 B dollars and entire of Korea is 1933 B dollars. 
In case of Apple, it is less than 3% - Apple's market capitalization is 869 B 
dollars, which is 2.9 % of total US stock market, on November 30, 2017.  
Accordingly, the stock value of Samsung Electronics has significant weight in 
KOSPI, the KOrea composite Stock Price Index. Even small fluctuation of Samsung 
Electronics solely can impact the whole market index. 
In this project we will try to understand the characteristics of Korea stock 
market, highlighting Samsung stock.   

* Market Capitalization or MarketCap is the total price of a company, 
calculated by the product of the count of the stock and the price of the stock.  
* The source of the data - Yahoo Finance, 
Kosis(Korea Staticstical Information Institute) and KRX(Korea Stock Exchange)  
* 3 CSV files were formed by calling API and downloading through Python codes.    
    1. samsung_electronics_20000104_20180321.csv  
      * 4592 observations x 7 variables  
      * Samsung Electronics stock price since 2000-01-04 using Yahoo Finance API  
    2. df_gross_market_cap_trend.csv  
      * 145 observations x 9 variables  
      * KOSPI market capitalization monthly trend since 2006-01, from Kosis    
    3. dfallcompanies.csv  
      * 2312 observations x 7 variables  
      * Company and ticker information in Korea stock market via KRX API.  
      * Samsung Electronics is just a single item of 2312 tickers but we can see 
      how big its market capitalization is with this data.  


# Univariate Plots Section

Let's look into each 3 CSV file.   

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

# rm(list=ls()) 

library(ggplot2)
library(dplyr)
```

Daily stock price and transaction volume of Samsung Electronics.  

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_samsung_csv}
dfsamsung <- read.csv("samsung_electronics_20000104_20180321.csv")
head(dfsamsung,5)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfsamsung, aes(dfsamsung$Adj.Close)) + 
  geom_histogram(binwidth = 100000)
```

The histogram says there are two groups of the stock price in hisory.  
However, because we alreay know it is stock price over time, the 2 
groups would reveal its true meaning in the flow of the time.    
Next. Check the price gap between open and close.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfsamsung, aes(dfsamsung$Open - dfsamsung$Close)) + 
  geom_histogram()

```

The gaps converge to zero. It might mean that the stock price of this company 
has been stable over time. However, the judge has to consider the time flow, 
so we would need bivariate analysis.  
Let's see the volume traded daily.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
g <- ggplot(dfsamsung, aes(dfsamsung$Volume)) + geom_histogram()
show(g)
gdata <- ggplot_build(g)
```

We can see there is a peak at volume = 226503, meaning the most frequently 
traded amount is about 226,503 daily. When we consider the total number of the 
stock 128,386,494, we can understand that the price of stock is set by the price 
of limited transactions, less than 0.18 % of total stock number here.  
Obviously, the whole stock is not sellable and buyable in one day, however, 
it is stunning finding to me that this small portion of the total stock 
determines the price.  

Let's move on to the next file, the trend of whole Korea stock market.  
When it is univariate analysis, one thing I have interest most here is turnnover 
rate, how much portion of the stock changed the ownership. That figure would 
provide some insight how much the market is in people's attention and interest.   

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_kospi_market_cap_trend_csv}
# Load the Data
dfmc_hist <- read.csv("df_gross_market_cap_trend.csv", header=TRUE, 
                      fileEncoding="UTF-8")
head(dfmc_hist,5)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfmc_hist, aes(dfmc_hist$turnover_rate_share)) + geom_histogram()
```

Notice that the time basis of the data is a month. Every month, about 35% of the 
total stock in Korea market has changed the ownership. Would that figure mean 
the ownership is way too rapidly changing? no idea for now.  We would need to 
compare that with US and Japan later.  
Now, let's see daily average flow of money between sellers and buyers.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfmc_hist, aes(dfmc_hist$traded_money_daily)) + geom_histogram()
# summary(dfmc_hist)
```

Mean value is roughly 7 B USD. When I consider that with 1933 B USD, the whole 
value of Korea stock market, we can notice just 0.4 % of total market share 
plays daily and determines the price. It looks consistent with the previous 
finding that Samsung stock price was also determined by only 0.18 % of total 
share daily,  
There are some occasions where daily money traded was way much like 
16,000,000,000,000 KRW (= 16 B USD rougly), more than twice of the mean value. 
When I see the date of the many transactions, 2009-05, 2011-07, 2018-01 
do not remind me of much for now.  

Now let's look into the 3rd CSV, all companies in Korea stock market.  

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_all_companies_in_KOSPI_csv}
dfallcompanies <- read.csv("dfallcompanies.csv", header=TRUE, 
                           fileEncoding = "UTF-8")
head(dfallcompanies, 5)

# the share count of Samsung, to calculate Market Cap later
samsung_share_count = dfallcompanies[
                        dfallcompanies$ticker == "005930",c("share_count")
                        ]
```

Samsung Electronics sits at the top. The raw data from KOSIS already calculated 
the market capitalization and its ratio to Korea entire. For the later use, 
the stock count of Samsung Electronics has been noted - 128386494.  
Histogram for market capitalization. 

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfallcompanies, aes(dfallcompanies$market_cap)) + 
  geom_histogram() 
```

In ordinary X-axis, the plot does not reveal much information. It is positively 
skewed extremely.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfallcompanies, aes(dfallcompanies$market_cap)) + 
  geom_histogram() +
  scale_x_log10()  
```

After applying log transformation, We can get market capitalization mostly sits 
between roughly 10 M USD and 1 B USD. Samsung and Hyundai are a few outliers at 
the right most, reaching around 300 B USD.  
Then, I want to check how diverse the share count.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(dfallcompanies, aes(dfallcompanies$share_count)) + 
  geom_histogram() +
  scale_x_log10()

```

X axis is also log transformed because it is posiviely skewed like market cap.  
We can see the stock count of each company ranges 1 M ~ 100 M mostly.  
Samsung is 128 M in the stock count positioning at the right-most.  


# Univariate Analysis

### What is the structure of your dataset?
1. samsung_electronics_20000104_20180321.csv  
  * 4592 observations x 7 variables  
2. df_gross_market_cap_trend.csv  
  * 145 observations x 9 variables  
3. dfallcompanies.csv  
  * 2312 observations x 7 variables  

### What is/are the main feature(s) of interest in your dataset?
1. samsung_electronics_20000104_20180321.csv  
  * 'Adj.Close' : Daily end price at closure. Market capitalization is 
  calculated by crossing this value and stock count.  
2. df_gross_market_cap_trend.csv  
  * 'gross_market_cap' : the market capitalization of the whole Korea stock 
  market.  
  * We will watch Samsung's value in the flow of total market, so this data 
  reveal how the main stream is flowing.  
3. dfallcompanies.csv  
  * 'market_cap_ratio' : the ratio of each company's market cap against the 
  whole Korea market.  

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
1. samsung_electronics_20000104_20180321.csv  
  * 'Volume' : the traded volume per a day, which might have association with 
  the price. For example, if the volume increases how it would impact the price? 
2. df_gross_market_cap_trend.csv  
  * 'turnover_rate_marketcap' : the proportion of the total stock that changed 
  the ownership might have some connection with the market cap trend.  
3. dfallcompanies.csv  
  * 'industry' : industry the company belongs to. This is the only categorical 
  variable in my datasets. Though we already have Korea total market trends, 
  industry segment that Samsung belongs to might be showing more granular 
  understanding.  


### Did you create any new variables from existing variables in the dataset?
Though not used for univariate analysis, Many viriables were created afterward.  
The first two datasets are time series datasets. When I imported the data into 
Rstudio, the 'date' was just recognized as string. So, I created a new variable 
that converted string date to date type. To examine seasonality, 
year and month were separated, to repeatedly show the stock price on the same 1 
~ 12 month axis. To normalize the value range, new variable was created to put 
standardized value in it.  
One challenge was that the 2nd dataset is monthly record of the past. 
To convert '2011-01' to date type, a day has to be specified. I inserted '-15' 
as the center of the month and converted the string to date type.  


### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
There was no unusual distribution according to univariate exploration. There are 
many outliers like Samsung and Hyundai, but they are the main subjects 
of this document.  
During the data preparation, the API at Korea goverment organization returned 
Korean variable name like '종목코드' and so on. I translated that to English.  
One tricky part was dfallcompanies.csv, because the data was orginally from 2 
data files according to the market - KOSPI and KOSDAQ in Korea. I concatenated 
the dataset to see the whole company landscape. For that, ticker code was 
reformatted as '005390' from '5390' for example, to support consistent code 
name.  



# Bivariate Plots Section

Because the first two datasets are time-series data. Univariate analysis might 
not be informative. Now we can put x-axis the date. 

First, stock price trends of Samsung Electronics.  
* 'Adj.Close' is adjusted price at close, usually same as 'Close'  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
# adding a new date type col
dfsamsung$date <- as.Date(dfsamsung$Date, "%Y-%m-%d")
# plot
ggplot(data=dfsamsung, mapping=aes(x=date, y=Adj.Close)) +
  geom_line(alpha=0.3, color="blue") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

I get that due to the good sales of Galaxy series, the stock price skyrocketed 
in recent years.  
It is time-series data. There might be seasonality.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
# first, separate year, month 
dfsamsung$year <- as.numeric(format(as.Date(dfsamsung$date),"%Y")) 
dfsamsung$month <- as.numeric(format(as.Date(dfsamsung$date),"%m"))
dfsamsung$month_day <- as.Date(paste("2000-", 
                                substring(dfsamsung$Date,6,10),sep="")
                               ,"%Y-%m-%d")
# plot
ggplot(data = dfsamsung, aes(x = month_day, y = Adj.Close, group = year, 
                             colour=as.factor(year))) + 
  geom_line() + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") 

```

It looks too noisy. Adding Smoothing.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(data = dfsamsung, aes(x = month_day, y = Adj.Close, group = year, 
                             colour=as.factor(year))) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") +
  geom_line(alpha=.2) + 
  geom_smooth() 

```

It is hard to detect any pattern because y range is wide. 
Applying standardization.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
# using dplyr
scale_this <- function(x) { (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE) }
dfsamsung_scaled <- 
  dfsamsung %>%
  group_by(year) %>%
  mutate(Std_Close = scale_this(Adj.Close),
         Std_Volume = scale_this(Volume))
ggplot(data=dfsamsung_scaled, aes(x=month_day, y=Std_Close, group=year, 
                                  colour=as.factor(year))) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") + 
  geom_line(alpha=.1) + 
  geom_smooth(alpha=.8) 

```

Still it looks random because of too many streams. So I picked years showing 
similar pattern.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
dfss <- subset(dfsamsung_scaled, year %in% 
                 c(2000,2001,2002,2004,2008,2010,2011,2012,2013,2014,2015))
ggplot(data = dfss, aes(x = month_day, y = Std_Close, group = year, 
                        colour=as.factor(year))) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") + 
  geom_line(alpha=.2) +
  geom_smooth(alpha=.8) 
```

Pattern 1 - decrease in summer and rise in winter, in year 2000,2001,2002, 2004,2008,2010,2011,2012,2013,2014,2015. I guess this cycle basically 
is the consistent power that boosted Samsung stock price. 
There might be some event repeatedly takes place every year. For example, 
it might be spree of new cell phone release. 
We would need more historical reference to find a clue.    

```{r echo=FALSE, message=FALSE, warning=FALSE, }
dfss <- subset(dfsamsung_scaled, year %in% c(2003,2005,2009,2016,2017))
ggplot(data = dfss, aes(x = month_day, y = Std_Close, group = year, 
                        colour=as.factor(year))) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") + 
  geom_line(alpha=.2) +
  geom_smooth(alpha=.8) 

```

Patter 2 - just up and up. These years need another research on why this 
accelration took place.  

Next, what about daily traded volume? 

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(data = dfsamsung, aes(x = date, y = Volume)) + 
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
  geom_line(alpha=.2) +
  geom_smooth(alpha=.8) 
```

Defying the price trend, the traded volume has been decreasing. It might be 
obvious, because the price soared and the price now is over 2000 USD per share. 
Small investors might not be able to engage the trade.  
Notably, during the global crisis started in 2008, the volume increased. 
Samsung stock price at that time was increasing, which indicates that 
investors bought Samsung during the crisis. They must have assumed that crisis 
was a chance to buy Samsung. If the stock wes bought in that period, the value 
would be x5 by now.  
  
I had a check on the seasonality of the volume after standardizing the value. 

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(data = dfsamsung_scaled, aes(x = month_day, y = Std_Volume, group=year, 
                                    colour=as.factor(year))) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") + 
  coord_cartesian(xlim=(as.Date(c("2000-01-01", "2000-12-01")))) + 
  geom_smooth(alpha=.2) 
```

I could not detect any pattern though I expected some boost around October, 
because we saw the pattern of rising price around that month in many years.   
  
Next, the trend of total market capitalization in KOSPI

```{r echo=FALSE, message=FALSE, warning=FALSE, }
# adding a new date type col
dfmc_hist$date <- as.Date(paste(dfmc_hist$year_month , "-15", sep=""), 
                          "%Y-%m-%d")
# plot
ggplot(data=dfmc_hist, mapping=aes(x=date, y=gross_market_cap)) +
  scale_x_date(date_labels = "%Y%m%d") + 
  geom_line(alpha=0.8)+ 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Acknowledgeably, the market capitalization of companies in Korea is escalating.  
Sudden drop in 2008 when the global crisis from Lehman Brothers bankruptcy took 
place, is recognizable as well.  
* Notice that it is not KOSPI, the Korea stock market index, but the total of 
market capitalization which we have interest in here.  

Now. Let's see whether there is seasonality in the records.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
# first, separate year, month 
dfmc_hist$year <- as.numeric(format(as.Date(dfmc_hist$date),"%Y")) 
dfmc_hist$month <- as.numeric(format(as.Date(dfmc_hist$date),"%m"))
dfmc_hist$month_day <- as.Date(paste("2000-", 
                                     substring(dfmc_hist$date,6,10),sep="")
                               ,"%Y-%m-%d")
# plot
ggplot(data = dfmc_hist, aes(x = month_day, y = gross_market_cap, group = year, 
                             colour=as.factor(year))) + 
  geom_line(alpha=0.2) +
  geom_smooth(alpha=0.2) +
  # geom_point() +
  # scale_x_discrete(breaks = dfmc_hist$month, labels = str(dfmc_hist$month))
  scale_x_date(date_breaks = "1 month", date_labels = "%m") 
```

Not much. let's check on the traded money. 

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(data=dfmc_hist, mapping=aes(x=date, y=traded_money_monthly)) +
  geom_line(alpha=0.3) + 
  geom_smooth() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

There is a big, 10-year-spanning wave. The market is approaching another peak 
now. This is not stock price but the traded money, but this surely implies the 
people's consideration of investing stock market. 
Accordingly we can guess the traded volume is increasing.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(data=dfmc_hist, mapping=aes(x=date, y=traded_volume_monthly)) +
  geom_line(alpha=0.3) + 
  geom_smooth() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

As expected.  
  
Now, let's look into the final dataset, all the companies listed in Korea stock 
market.  
When I ordered the data by the market capitalization ratio. the plot is just as 
I heard of. Samsung is overwhelming.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
dfallcompanies_subset <- subset(dfallcompanies, market_cap_ratio >= 0.01)
dfallcompanies_subset <- dfallcompanies_subset[
                order(dfallcompanies_subset$market_cap_ratio, decreasing = T),]
dfallcompanies_subset$ticker_nm_eng <- 
  c('Sammsung Elec.','SK hynix','Celltrion','Samsung Elec.P','Hyundai Motors',
    'Samsung Biologics','POSCO','LG Chemical','KB finance','Naver',
    'Samsung Construction','Samsung Life','Hyundai Mobis','SK','Shinhan group',
    'KEPCO','Samsung SDS','SK innovation')
ggplot(data=dfallcompanies_subset,mapping=aes(x=ticker_nm,y=market_cap_ratio))+
  geom_bar(stat="identity", fill="dark blue") +
  aes(x=reorder(ticker_nm_eng,-market_cap_ratio),y=market_cap_ratio,
      label=market_cap_ratio) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

There are many companies' name starting with 'Samsung'. They could be assumed 
a single company, Samsung. 
Then their market cap ratio might surpass 0.3 of the total Korea stock market. 
The ownership of that group companies are known to be very complicated and 
blurry at the edge. So, it would be next time to separate all the Samsung 
family companies and its market capitalization.  

Now let's group by industry to see how diverse the indsutry and how we can 
characterize Korea industries. 

```{r echo=FALSE, message=FALSE, warning=FALSE, }
dfallcompanies_group <- 
  dfallcompanies %>%
  group_by(industry) %>%
  summarise(market_cap_ratio_sum = sum(market_cap_ratio),n=n())
dfallcompanies_group <- dfallcompanies_group[
                order(dfallcompanies_group$market_cap_ratio_sum, 
                      decreasing = T),]
dfallcompanies_group <- dfallcompanies_group[
  dfallcompanies_group$market_cap_ratio_sum  > 0.01,]
dfallcompanies_group$industry_eng <- 
  c("Communiation Device","BFSI","Biochemicals","Semiconductor",
    "Basic Chemicals", "Insurance",
    "Other Chemicals","ETC","Medicine","Car manufacturing","Iron","WholeSale",
    "Software","Internet service","Electronic Parts","Car parts","Tele comm.",
    "Retail","Financial Support","System Integration","Special Machines",
    "ETC Food","Bank","Electricity")
ggplot(data=dfallcompanies_group, 
       mapping=aes(x=industry,y=market_cap_ratio_sum), 
       group=industry, color=as.factor((industry))) + 
  geom_bar(stat="identity", fill="dark blue") +
  aes(x=reorder(industry_eng,-market_cap_ratio_sum),y=market_cap_ratio_sum,
      label=market_cap_ratio_sum) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

1st item is, to simply put, cell phone manufacturing industry where Samsung 
belongs to. Samsung is core part of the industry according to the ratio. It is 
same as Samsung alone.  
Other industries are much lower. So, when it comes to stability, the landscape 
of Korea industry is fragile or weak at risk in my view, because the whole 
economy is too much relying on Samsung and its export of non-diverse products.  
I get that conventional manufacturing industry is decreasing. Rather the 
financial service like bank and insurance is taking much part, 10%. Software in 
IT is weak, compared to hardware like semiconductor, LED display.   


# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?  
In the bivariate exploration, I could not directly compare the total market 
value and that of Samsung on the same time axis, but each plot 
gave me interesting view point.  1. Samsung stock price over time revealed 
there could be a cycle  2. Total Korea market revealed there is a big cycle 
which is approaching another peak.  3. Korea industry is unbalanced.    

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?  
One thing I clearly found is that the price of stock and traded volume go 
the opposite. I would be obvious that expensive stock is not easy to trade, 
but I verified that it is true.  
And there might be seasonality in the stock price. I noticed a Samsung 
stock flow repeating every year, not that assertive though. I need paper work 
to see what was behind such cycling.  

### What was the strongest relationship you found?
Traded money and traded volume have much in common in the trend. It would be 
much clearer once we put them on the same plot in multivariate analysis.  
And I got investment ideas using the finding that there seems to be a cycle in 
Samsung stock. Besides, there seems to be a 10-year-spanning cycle in total 
Korea stock market.  



# Multivariate Plots Section

Now, let's put Samsung and the whole Korea market together.   

```{r echo=FALSE, message=FALSE, warning=FALSE, }
# samsung_share_count is 128386494
ggplot(data=dfsamsung, mapping=aes(x=dfsamsung$date, 
                                   y=Adj.Close*samsung_share_count)) +
  geom_line(alpha=0.3, color="blue") + 
  geom_line(data=dfmc_hist, mapping=aes(x=dfmc_hist$date, y=gross_market_cap), 
            color="black") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

```

OK. we can see Samsung might have much portion against the whole stock market 
but not sure it is around 0.1 or 0.3 along with the time. Let's clarify that 
by calculating the ratio over the time. 

```{r echo=FALSE, message=FALSE, warning=FALSE, }
dfsamsung.monthly_avg <- 
                dfsamsung %>% 
                group_by(year, month) %>% 
                summarise(
                  monthly_price_avg = mean(Adj.Close), 
                  monthly_marketcap_avg = mean(Adj.Close*samsung_share_count), 
                  monthly_volume = sum(Volume), 
                  n=n())
dfsamsung.monthly_avg$date <- as.Date(ISOdate(dfsamsung.monthly_avg$year, 
                                              dfsamsung.monthly_avg$month, 15)) 
dfsamsung.monthly_marketcap_ratio <- merge(dfsamsung.monthly_avg, dfmc_hist, 
                                           by=c("year", "month"))
dfsamsung.monthly_marketcap_ratio$ratio <- 
  (dfsamsung.monthly_marketcap_ratio$monthly_marketcap_avg  / dfsamsung.monthly_marketcap_ratio$gross_market_cap )
dfsamsung.monthly_marketcap_ratio$date <- 
  as.Date(ISOdate(dfsamsung.monthly_marketcap_ratio$year, 
                  dfsamsung.monthly_marketcap_ratio$month, 15)) 

# plot
ggplot(data=dfsamsung.monthly_marketcap_ratio, 
       mapping=aes(x=dfsamsung.monthly_marketcap_ratio$date, 
                   y=dfsamsung.monthly_marketcap_ratio$ratio)) + 
  geom_line(alpha=0.3, color="red", size=2) +
  scale_x_date(date_breaks = "6 month", date_labels = "%Y.%m") +
  geom_line(data=subset(dfsamsung.monthly_avg, 
                        year > 2005 & year < 2018), 
            mapping=aes(x=date, y=monthly_marketcap_avg/(10^15*3)+0.09), 
            color="blue", alpha=0.5) +
  geom_line(data=dfmc_hist, mapping=aes(x=dfmc_hist$date, 
                                        y=gross_market_cap/10^16+0.04), 
            color="black") +
  labs(title="The trend of Samsung ratio", 
       x="Year.Month", 
       y="Market Cap Ratio") +
  annotate("text", x = as.Date("2015-10-01"), y = 0.20, color="black", 
           label = "Korea") +
  annotate("text", x = as.Date("2015-10-01"), y = 0.16, color="blue", 
           label = "Samsung") +
  annotate("text", x = as.Date("2015-10-01"), y = 0.12, color="red", 
           label = "ratio") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 90, hjust = 1)) 
```

This plot depicts how the big ratio of Samsung Electronics against the whole 
Korea stock market has been established. As expected, the more recent the 
bigger ratio but there are several interesting parts.  
1. There seems to be a cycle in the plot, spanning about 4 years. In other 
words, Samsung stock boosted every 4 years. I don't think the stock price 
solely can reveal this cycle.  
2. There is a deep pit nearing zero in 2007~2008. I guess it overlaps the 
global crisis and the date is much interesting - the drop was already made 1 
year aheady of the crisis. Let's zoom in that part, with other trends 
overlapped as reference.  

```{r echo=FALSE, message=FALSE, warning=FALSE, }
ggplot(data=dfsamsung.monthly_marketcap_ratio, 
       mapping=aes(x=dfsamsung.monthly_marketcap_ratio$date, 
                   y=dfsamsung.monthly_marketcap_ratio$ratio)) + 
  geom_line(alpha=0.3, color="red", size=2) + 
  coord_cartesian(xlim=(as.Date(c("2007-01-01", "2012-01-01"))), 
                  ylim=c(0.05,0.170)) + 
  scale_x_date(date_breaks = "3 month", 
               date_labels = "%Y.%m") +
  geom_line(data=subset(dfsamsung.monthly_avg, 
                        year %in% c(2007,2008,2009,2010,2011)), 
            mapping=aes(x=date, y=monthly_marketcap_avg/10^15+0.04), 
            color="blue", alpha=0.5) +
  geom_line(data=dfmc_hist, mapping=aes(x=dfmc_hist$date, 
                                        y=gross_market_cap/10^16+0.04), 
            color="black") +
  labs(title="Zooming in the Ratio of Samsung", 
       subtitle="Market Cap ratio of Samsung to the whole Korea stock market", 
       x="Year.Month", 
       y="Market Cap Ratio") +
  annotate("text", x = as.Date("2007-10-01"), y = 0.16, color="black", 
           label = "Korea whole market cap.") +
  annotate("text", x = as.Date("2007-10-01"), y = 0.097, color="blue", 
           label = "Samsung market cap.") +
  annotate("text", x = as.Date("2007-10-01"), y = 0.07, color="red", 
           label = "Ratio") +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 90, hjust = 1)) 

```

The Lehman Brothers bankruptcy broke out in September 2008. The two other lines, 
market cap of Korea (black) and market cap of Samsung (blue), both dropped 
just after that period. However, the market cap ratio at that time already was 
climbing up after the drop 1 year ago.  


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?
This is stock market data where people's collective mind is playing everywhere, 
there would not be variables which show strong relationship like physics.  
Rather, I could see some cycle over time. 1) Samsung's money absorbing cycle 
every 4 years. 2) 10 years cycle of Korea stock market. These two might be 
useful guide for investment.  


### Were there any interesting or surprising interactions between features?
Most surprising was mismatched timing of the trends of price and market cap 
ratio. Seemingly price is a superficial metric and more essential part might be 
market cap ratio which already made a motion and direction before certain price 
forms. Of course, more data and research would be required.  


### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.
The 2 cycles, 4 years of Samsung and 10 years of Korea, could be the candidates 
of the model. We would need more data to verify that.  


# Final Plots and Summary

### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_One}
ggplot(data=dfsamsung.monthly_marketcap_ratio, 
       mapping=aes(x=dfsamsung.monthly_marketcap_ratio$date, 
                   y=dfsamsung.monthly_marketcap_ratio$ratio) ) + 
  geom_line(alpha=0.3, color="red", size=2) + 
  # coord_cartesian(xlim=(as.Date(c("2007-01-01", "2012-01-01"))), ylim=c(0.05,0.170)) + 
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  geom_line(data=subset(dfsamsung.monthly_avg, year > 2006 & year < 2018), 
            mapping=aes(x=date, y=scale_this(monthly_marketcap_avg)/20), 
            color="blue", 
            alpha=0.5) +
  geom_line(data=dfmc_hist, mapping=aes(x=dfmc_hist$date, 
                                        y=scale_this(gross_market_cap)/20+0.05), 
            color="black") +
  labs(title="The Ratio of Samsung", 
       subtitle="Market Cap ratio of Samsung to the whole Korea stock market", 
       x="Year", 
       y="Market Cap Ratio") +
  annotate("text", x = as.Date("2014-11-01"), y = 0.05, color="black", 
           label = "Korea whole market cap.") +
  annotate("text", x = as.Date("2014-11-01"), y = -0.01, color="blue", 
           label = "Samsung market cap.") +
  annotate("text", x = as.Date("2014-11-01"), y = 0.14, color="red", 
           label = "Ratio") +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 90, hjust = 1)) 
```

### Description One  
The current ratio of Samsung Electronics' market value against the entire Korea 
stock market is 17%. It is huge portion. Then what about the ratio in the past? 
In this project I tracked the trend of the ratio over time.  
In the plot, red line is the ratio ranging 0.05 ~ 0.20. Black line indicates the 
entire market capitalization of Korea stock market and blue line corresponds to 
Samsung Electronics' market capitalization. Later two lines are just showing 
overall trends, irrelavant to the y-axis unit.  
The red line shows a cycling pattern of the ratio, repeating every 4 years. 
When we see black and blue lines, the moment that the ratio hit the lowest points, 
the gap between black and blue is widest. In my interpretation, Samsung's value 
boosts up 1 year later of a big influx of money into the Korea stock market. 
It looks like pumping water into a lake which in fact is mostly shallow but has 
big depth area called Samsung. This plot is impressive to me because that implies 
not just the weight of Samsung in Korea but also how they behave each other over 
time.  
The intial money influx was not targeting Samsung according to the plot, then 
what company would that be? further research is required.  


### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}
dfss <- subset(dfsamsung_scaled, 
          year %in% c(2000,2001,2002,2004,2008,2010,2011,2012,2013,2014,2015))
ggplot(data = dfss, aes(x = month_day, y = Std_Close, group = year, 
                        colour=as.factor(year))) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m") + 
  # coord_cartesian(xlim=(as.Date(c("2000-08-01", "2000-12-01")))) +
  geom_line(alpha=.2) +
  geom_smooth(alpha=.5) +
  labs(title="Seasonality in Samsung Stock Price", x="Month", 
       y="Stock Price, Standardized") +
  labs(color='Year')  +
  theme(plot.title = element_text(hjust = 0.5)) 
  
```

### Description Two
The reason I am interested in this plot is that this might be a clue to invest 
Samsung better. Of course we already checked other pattern exist but the above 
looks prominent and frequent. There might be some reason behind, for example 
rolling out new product aiming at certain season.  


### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}
ggplot(data=dfmc_hist, mapping=aes(x=date, y=traded_money_monthly)) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
  geom_line(alpha=0.3) + 
  geom_smooth() +
  labs(title="Money Tide over 10 years", 
       subtitle="Cycling pattern of money flow in Korea stock market", 
       x="Year", y="Monthly Traded Money (KRW)") +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5)) 

```

### Description Three
Together with the traded volume plot which has the same pattern, this plot 
might be able to guide investors how the landscape is changing. 
It totally feels like tide. Presently people are shifting their wealth over to 
stock market, then from where? real estate maybe? Another research would be 
required.  


# Reflection

Main focus here is the ratio of Samsung's value against total value of Korea 
stock market over time. During the exploration, there were other interesting 
findings not just the shape of the ratio plot. One thing most impressive 
is that the ratio could become a guide for investors because certain cycle was 
detected and the ratio pattern preceded ahead of the price. Validation is 
necessary of course.  
About 60% of the time was spent to prepare the data, 3 files. Adapting to Yahoo 
Finance API was most tedious part because of my limited knowledge on stock 
market and weak documentation of Yahoo Finance. I heavily relied on many blogs.  
My exploration and analysis are lack of generalization. The pattern and cycle I 
found have to be validated with other data such as other company data like 
Hyundai, LG, and other global companies in each stock market. That will be 
the future items for research.  
During the exploration, again I realized that R is easy, quick and intuitive. 
Because Python has been in my comfort zone, I searched Python equivalent to 
ggplot library and found "plotnine" 
(http://pltn.ca/plotnine-superior-python-ggplot/). The feature 
and grammar is the same and I will use that library in my other projects at 
early stage of data exploration .  


### References   
*	Samsung Electronics on Yahoo Finance : https://finance.yahoo.com/quote/005935.KS?p=005935.KS
*	Yahoo Finance and python, guide : https://ntguardian.wordpress.com/2016/09/19/introduction-stock-market-data-python-1/
*	Korea stock index, KOSPI historical data download : http://kosis.kr/statHtml/statHtml.do?orgId=343&tblId=DT_343_2010_S0001#
*	Company information in KOSPI, KOSDAQ : www.krx.co.kr
*	Plotting seasonality : https://stackoverflow.com/questions/13520639/ggplot-year-by-year-comparison
*	Value standardization : https://stackoverflow.com/questions/35775696/trying-to-use-dplyr-to-group-by-and-apply-scale



